---
title: "PA1_template"
author: "Diego André Genaro García Méndez"
date: "21/9/2020"
output: html_document
---

1.Code for reading in the dataset and/or processing the data

```{r}

setwd("C:/Users/Diego/Documents/Cosas utiles de R/repdata_data_activity")
data<-read.csv("activity.csv")
```

2.Histogram of the total number of steps taken each day
```{r}
library(dplyr)
totalperday<- data %>% group_by(date) %>% summarise(totalday=sum(steps))

hist(totalperday$totalday)

```

3.Mean and median number of steps taken each day

```{r}
meanmedian<- data %>% group_by(date) %>% summarise(mean=mean(steps),median=median(steps))
head(meanmedian)
```

4. series plot of the average number of steps taken
```{r}
library(ggplot2)
meanmedian$date<-as.Date(meanmedian$date)
meanmedian %>%
  ggplot( aes(x=date, y=mean)) +
    geom_line() +
    geom_point()
```

5.The 5-minute interval that, on average, contains the maximum number of steps

```{r}
max<-max(data$steps,na.rm=T)
data[max,3]
```
6.Code to describe and show a strategy for imputing missing data

In this case a will use tha mean for imputing the missing data.
And number of missing values

```{r}

mean<-mean(data$steps,na.rm=T)
missing<-is.na(data$steps)
newdata<-data
newdata[missing,1]<-mean
numberna<-sum(is.na(data$steps))
numberna
```

7.Histogram of the total number of steps taken each day after missing values are imputed

```{r}
totalperday<- newdata %>% group_by(date) %>% summarise(totalday=sum(steps))

hist(totalperday$totalday)
```

8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
avg<- data %>% group_by(date) %>% summarise(mean=mean(steps))
day<-weekdays(as.Date(avg$date))

weekday<-factor(day %in% c("lunes","martes","miércoles","jueves","viernes"),levels=c(FALSE, TRUE), labels=c('weekend', 'weekday'))
dataday<-cbind(avg,weekday) 

par(mfrow=c(2,1))


plot(dataday[dataday$weekday=='weekday',2],type = "l",main = 'weekday')
plot(dataday[dataday$weekday=='weekend',2],type = "l",main='weekend')
```

